---
title: "Thesis Appendix"
author: "Sophia Freuden"
date: "4/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(imager)
library(tidyverse)
```

<center><b><h1>Figures for English Language Stories</h1></b></center>
<center><i>Scroll down to find Russian and German language figures for each individual.</i></center>
<br>
<center><h2>Soros</h2></center>

```{r, fig.align='center', fig.height=10, fig.width=10}
img1 <- load.image("all-soros/all-soros.png")

plot(img1, axes = FALSE, main = "Word Cloud")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img2 <- load.image("all-soros/emo1.png")

plot(img2, axes = FALSE, main = "Emotion Analysis")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img3 <- load.image("all-soros/table1.png")

plot(img3, axes = FALSE, main = "Sentiment Analysis")
```

<center><h3>Frequency Plots for Individual Terms</h3></center>
<center>Images ordered as terms discussed in thesis.</center>

```{r, fig.align='center', fig.height=10, fig.width=10}
img4 <- load.image("all-soros/clinton.png")

plot(img4, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img5 <- load.image("all-soros/democraci.png")

plot(img5, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img6 <- load.image("all-soros/democrat.png")

plot(img6, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img7 <- load.image("all-soros/democratic.png")

plot(img7, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img8 <- load.image("all-soros/elect.png")

plot(img8, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img9 <- load.image("all-soros/europe.png")

plot(img9, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img10 <- load.image("all-soros/european.png")

plot(img10, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img11 <- load.image("all-soros/fidesz.png")

plot(img11, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img12 <- load.image("all-soros/hungary.png")

plot(img12, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img13 <- load.image("all-soros/immigr.png")

plot(img13, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img14 <- load.image("all-soros/liber.png")

plot(img14, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img15 <- load.image("all-soros/media.png")

plot(img15, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img16 <- load.image("all-soros/migrant.png")

plot(img16, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img17 <- load.image("all-soros/orban.png")

plot(img17, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img18 <- load.image("all-soros/protest.png")

plot(img18, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img19 <- load.image("all-soros/putin.png")

plot(img19, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img20 <- load.image("all-soros/republican.png")

plot(img20, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img21 <- load.image("all-soros/trump.png")

plot(img21, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img22 <- load.image("all-soros/ukrain.png")

plot(img22, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img23 <- load.image("all-soros/war.png")

plot(img23, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img24 <- load.image("all-soros/western.png")

plot(img24, axes = FALSE, main = "")
```

<br>
<center><h2>Clinton</h2></center>

```{r, fig.align='center', fig.height=10, fig.width=10}
imgA <- load.image("all-clinton/all-clinton.png")

plot(img1, axes = FALSE, main = "Word Cloud")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
imgB <- load.image("all-clinton/emo1.png")

plot(img2, axes = FALSE, main = "Emotion Analysis")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
imgC <- load.image("all-clinton/table1.png")

plot(img3, axes = FALSE, main = "Sentiment Analysis")
```

<center><h3>Frequency Plots for Individual Terms</h3></center>
<center>Images ordered as terms discussed in thesis.</center>

```{r, fig.align='center', fig.height=10, fig.width=10}
img25 <- load.image("all-clinton/elect.png")

plot(img25, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img26 <- load.image("all-clinton/european.png")

plot(img26, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img27 <- load.image("all-clinton/foreign.png")

plot(img27, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img28 <- load.image("all-clinton/georgia.png")

plot(img28, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img29 <- load.image("all-clinton/magnitsky.png")

plot(img29, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img30 <- load.image("all-clinton/media.png")

plot(img30, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img31 <- load.image("all-clinton/militari.png")

plot(img31, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img32 <- load.image("all-clinton/nato.png")

plot(img32, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img33 <- load.image("all-clinton/protest.png")

plot(img33, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img34 <- load.image("all-clinton/republican.png")

plot(img34, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img35 <- load.image("all-clinton/ukrain.png")

plot(img35, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img36 <- load.image("all-clinton/war.png")

plot(img36, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img37 <- load.image("all-clinton/western.png")

plot(img37, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img38 <- load.image("all-clinton/democraci.png")

plot(img38, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img39 <- load.image("all-clinton/democrat.png")

plot(img39, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img40 <- load.image("all-clinton/democratic.png")

plot(img40, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img41 <- load.image("all-clinton/europe.png")

plot(img41, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img42 <- load.image("all-clinton/influenc.png")

plot(img42, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img43 <- load.image("all-clinton/putin.png")

plot(img43, axes = FALSE, main = "")
```

<br>
<center><h2>McFaul</h2></center>

```{r, fig.align='center', fig.height=10, fig.width=10}
img44 <- load.image("all-mcfaul/all-mcfaul.png")

plot(img44, axes = FALSE, main = "Word Cloud")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img45 <- load.image("all-mcfaul/emo1.png")

plot(img45, axes = FALSE, main = "Emotion Analysis")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img46 <- load.image("all-mcfaul/table1.png")

plot(img46, axes = FALSE, main = "Sentiment Analysis")
```

<center><h3>Frequency Plots for Individual Terms</h3></center>
<center>Images ordered as terms discussed in thesis.</center>

```{r, fig.align='center', fig.height=10, fig.width=10}
img47 <- load.image("all-mcfaul/browder.png")

plot(img47, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img48 <- load.image("all-mcfaul/democraci.png")

plot(img48, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img49 <- load.image("all-mcfaul/media.png")

plot(img49, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img50 <- load.image("all-mcfaul/nato.png")

plot(img50, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img51 <- load.image("all-mcfaul/clinton.png")

plot(img51, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img52 <- load.image("all-mcfaul/democrat.png")

plot(img52, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img53 <- load.image("all-mcfaul/influenc.png")

plot(img53, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img54 <- load.image("all-mcfaul/magnitsky.png")

plot(img54, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img55 <- load.image("all-mcfaul/republican.png")

plot(img55, axes = FALSE, main = "")
```

<center><b><h1>Figures for Russian Language Stories</h1></b></center>
<center><i>Scroll down to find German language figures for each individual.</i></center>
<br>
<center><h2>Soros</h2></center>

```{r, fig.align='center', fig.height=10, fig.width=10}
img56 <- load.image("all-soros/Russian/all-soros.png")

plot(img56, axes = FALSE, main = "Word Cloud")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img57 <- load.image("all-soros/Russian/table1.png")

plot(img57, axes = FALSE, main = "Sentiment Analysis")
```

<center><h3>Frequency Plots for Individual Terms</h3></center>
<center>Images ordered as terms discussed in thesis.</center>

```{r, fig.align='center', fig.height=10, fig.width=10}
img58 <- load.image("all-soros/Russian/eu.png")

plot(img58, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img59 <- load.image("all-soros/Russian/hungary2.png")

plot(img59, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img60 <- load.image("all-soros/Russian/media.png")

plot(img60, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img61 <- load.image("all-soros/Russian/trump.png")

plot(img61, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img62 <- load.image("all-soros/Russian/clinton.png")

plot(img62, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img63 <- load.image("all-soros/Russian/democracy.png")

plot(img63, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img64 <- load.image("all-soros/Russian/elections2.png")

plot(img64, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img65 <- load.image("all-soros/Russian/foreign4.png")

plot(img65, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img66 <- load.image("all-soros/Russian/migrants2.png")

plot(img66, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img67 <- load.image("all-soros/Russian/nato.png")

plot(img67, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img68 <- load.image("all-soros/Russian/ngo2.png")

plot(img68, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img69 <- load.image("all-soros/Russian/orban.png")

plot(img69, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img70 <- load.image("all-soros/Russian/party.png")

plot(img70, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img71 <- load.image("all-soros/Russian/ukraine3.png")

plot(img71, axes = FALSE, main = "")
```

<center><h2>Clinton</h2></center>

```{r, fig.align='center', fig.height=10, fig.width=10}
img72 <- load.image("all-clinton/Russian/all-clinton.png")

plot(img56, axes = FALSE, main = "Word Cloud")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img73 <- load.image("all-clinton/Russian/table1.png")

plot(img73, axes = FALSE, main = "Sentiment Analysis")
```

<center><h3>Frequency Plots for Individual Terms</h3></center>
<center>Images ordered as terms discussed in thesis.</center>

```{r, fig.align='center', fig.height=10, fig.width=10}
img74 <- load.image("all-clinton/Russian/democracy.png")

plot(img74, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img75 <- load.image("all-clinton/Russian/eu.png")

plot(img75, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img76 <- load.image("all-clinton/Russian/france.png")

plot(img76, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img77 <- load.image("all-clinton/Russian/media.png")

plot(img77, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img78 <- load.image("all-clinton/Russian/nato.png")

plot(img78, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img79 <- load.image("all-clinton/Russian/putin.png")

plot(img79, axes = FALSE, main = "")
```

```{r, fig.align='center', fig.height=10, fig.width=10}
img80 <- load.image("all-clinton/Russian/soros.png")

plot(img80, axes = FALSE, main = "")
```












